% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage{fancyvrb}
\usepackage{color}
\usepackage{framed}

% Gray background for code chunks
\definecolor{shadecolor}{rgb}{0.97,0.97,0.97}

% Define CodeChunk as a shaded box
\newenvironment{CodeChunk}{\begin{snugshade}}{\end{snugshade}}

% Define Highlighting for source code
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{fontsize=\small,commandchars=\\\{\}}

% Define Output for printed results
\DefineVerbatimEnvironment{Output}{Verbatim}{fontsize=\small}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Pacifism and Antimilitarism in Japan},
  pdfauthor={Jozef Rivest},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Maroon},
  urlcolor={Maroon},
  pdfcreator={LaTeX via pandoc}}


\title{Pacifism and Antimilitarism in Japan}
\author{Jozef Rivest}
\date{Invalid Date}

\begin{document}
\maketitle


\clearpage
\tableofcontents

\clearpage

\section{Introduction}\label{introduction}

The present document introduce the codebook for the following dataset.
For an exemple of the entry in the dataset, please refer to the code
chunk below.

\begin{CodeChunk}
\begin{Highlighting}{}
print(mil_bases)\end{Highlighting}
    region      city personel type size prop\_size longitude latitude
1 Kanagawa  Yokosuka    24000    0  568       0.2  35.29249 139.6696
2   Aomori Hachinohe    24000    0  568       0.2  35.29249 139.6696
\end{CodeChunk}

\section{Region}\label{region}

\texttt{region} here refers to the administrative region where the
military base is located. The term region is employed here as the
denomination depends for each country. See the list below to understand
what \texttt{region} corresponds to for each country present in the
dataset.

\begin{itemize}
\tightlist
\item
  Japan \(\rightarrow\) Prefectures
\end{itemize}

\section{City}\label{city}

\texttt{city} corresponds to the city where the base is situated.

\section{Personel}\label{personel}

\section{Type}\label{type}

The \texttt{type} refers to the type of forces the base is hosting. As
bases can host more than one group forces, a numerical value is assigned
to each to account also for combinations.

\section{Size}\label{size}

\texttt{personel} corresponds to the total number of working personel
officially recensed.

\section{Proportion Size}\label{proportion-size}

The \texttt{prop\textbackslash{}\_size} variable corresponds to the
ratio of the total area of the base over the total area of the city
where the base is located.

\section{Longitude}\label{longitude}

The \texttt{longitude} variable corresponds to the longitude location of
the base. Positive value indicates the location north of the equator
line, and negative values means location south of the equator line.

\section{Latitude}\label{latitude}

The \texttt{latitude} is a variable that locates the latitude location
of the base.




\end{document}
