---
author: Jozef Rivest
bibliography: ../paper/references.bib
date: " "
format:
  pdf:
    documentclass: article
    font-size: 12pt
    linkcolor: Maroon
    citecolor: Maroon
    urlcolor: Maroon
    keep-tex: true
    include-in-header: header.tex

title: Pacifism and Antimilitarism in Japan
---


```{r}
#| include: false

source("../code/dataset.R")

knitr::knit_hooks$set(
  source = function(x, options) {
    paste0("\\begin{CodeChunk}\n\\begin{Highlighting}{}\n",
           x,
           "\\end{Highlighting}\n")
  },
  output = function(x, options) {
    paste0(x, "\\end{CodeChunk}\n")
  }
)
```

\clearpage
\tableofcontents

\clearpage

# Introduction

The present document introduce the codebook for the following dataset.
For an exemple of the entry in the dataset, please refer to the code
chunk below.


```{r}

print(mil_bases)
```

# Region

`region` here refers to the administrative region where the military
base is located. The term region is employed here as the denomination
depends for each country. See the list below to understand what `region`
corresponds to for each country present in the dataset.

-   Japan $\rightarrow$ Prefectures

# City

`city` corresponds to the city where the base is situated.

# Personel

# Type

The `type` refers to the type of forces the base is hosting. As bases
can host more than one group forces, a numerical value is assigned to
each to account also for combinations.

<!-- ::: tblr -->
<!-- colspec=Q\[\]Q\[\], row1=font=**,**, cell2-32=halign=c,, Type & Value\ -->
<!-- Naval Base & 0\ -->
<!-- Ground Base & 1\ -->
<!-- ::: -->

# Size

`personel` corresponds to the total number of working personel
officially recensed.

# Proportion Size

The `prop\_size` variable corresponds to the ratio of the total area of
the base over the total area of the city where the base is located.

# Longitude

The `longitude` variable corresponds to the longitude location of the
base. Positive value indicates the location north of the equator line,
and negative values means location south of the equator line.

# Latitude

The `latitude` is a variable that locates the latitude location of the
base.
